### 2015-07-28 Irregular-occ/Irregular-occ.tex
.

Since their sizes are very small (see table \ref{} \textcolor{red}{Ainda vou fazer a tabela}), predict the exact location and instant where the shadow will cross the Earth demands a good precision. For instance, the bigger irregular satellite of Jupiter has an estimated size of 150 km \citep{Porco2003}, which is equivalent to an apparent size of 40 mas, must have an error smaller than its size for being observable. For the other objects, smaller or farther than Himalia, the situation is more difficult.

@@

We utilize the offsets obtained by \cite{GomesJunior2015} to identify a pattern in the error of the ephemeris. This pattern could be used to extrapolate an offset to the satellite by the time of the occultation predicted. Plots of the offsets over time and true anomaly (see Fig. \ref{} for ??) clearly show that these two parameters are the most important in the differences observed.

>>>>

Since their estimated sizes are very small (see table \ref{} \textcolor{red}{Ainda vou fazer a tabela}), predict the exact location and instant where the shadow will cross the Earth demands a good precision. For instance, the bigger irregular satellite of Jupiter has an estimated size of 150 km \citep{Porco2003}, which is equivalent to an apparent size of 40 mas, must have an error smaller than its size for being observable. For the other objects, smaller or farther than Himalia, the situation is more difficult.

@@

We utilize the offsets obtained by \cite{GomesJunior2015} to identify a pattern in the error of the ephemeris. This pattern could be used to extrapolate an offset to the satellite by the time of the occultation predicted. Plots of the offsets over time and true anomaly (see Fig. \ref{Fig:offxtime} and \ref{Fig:offxtanom} for Carme) clearly show that these two parameters are the most important in the differences observed.

\begin{figure}
\begin{centering}
\includegraphics[scale=0.25]{figures/DEC.png}\label{Fig:offxtime}
\caption{Offsets of the declination of Carme by time. \textcolor{red}{Figura só para visualização, vou colocar alguma melhor depois}}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[scale=0.25]{figures/DEC_anom.png} \label{Fig:offxtanom}
\caption{Offsets of the declination of Carme by true anomaly. \textcolor{red}{Figura só para visualização, vou colocar alguma melhor depois}}
\end{centering}
\end{figure}

\begin{equation}
F(t,f) = p[0]\times \frac{t - jd_{0}}{365.65} + p[1]\times \sin(f) + p[2]\times\cos(f) + p[3],
\label{eq:linear}
\end{equation}

\begin{equation}
\begin{split}
%F = \{F_{x} \in  F_{c} &: (|S| > |C|) \\
% &\quad \cap (\text{minPixels}  < |S| < \text{maxPixels}) \\
% &\quad \cap (|S_{\text{conected}}| > |S| - \epsilon) \}
F(t,f) = p[0]\times\sin\left(\frac{2\pi}{p[1]}\times \frac{t - jd_{0}}{365.25} + p[2]\right) + p[3]\times\sin(f) + \\ +p[4]\times\cos(f) + p[5],
\end{split}
\end{equation}
